|

### 2020-01-12 nontex/install/git/fs_git_setup.Rmd
repo pull bash update, sublime to path

to create bash file to store these (from git bash in windows):

@@

# create bash file
vim pull_repos
vim push_repos

# paste the text below over, comfirm bash loc with: which bash
#!/usr/bin/bash
echo start fan github pull
# Security
eval "$(ssh-agent)"
ssh-add ~/.ssh/id_rsa
# Pull from Persistent Repos
cd ~/fanwangecon.github.io
git pull github master
# Stop Secured SSH
kill $SSH_AGENT_PID

# change permission to make file an executable
chmod u+x ~/PyFan/bin/pull_repos
chmod u+x ~/PyFan/bin/push_repos
# execute script
bash ~/PyFan/bin/pull_repos
```

>>>>

to create bash file to store these (from git bash in windows), generate a pull_repos and push_repos file.

@@

# create bash file
vim pull_repos
vim push_repos
```

What *pull_repos* could look like, *push_repos* will look similar:

```{bash}
# paste the text below over, comfirm bash loc with: which bash
#!/usr/bin/bash
echo start fan github pull

# Security, will prompt for password once.
eval "$(ssh-agent)"
ssh-add ~/.ssh/id_rsa

# Pull from Persistent Repos
cd ~/fanwangecon.github.io
git pull github master
cd ~/PyFan
git pull github master
cd ~/Teaching
git pull github master

# Stop Secured SSH
kill $SSH_AGENT_PID

# Open Atom with the Projects
atom ~/fanwangecon.github.io ~/PyFan ~/Teaching
```

Possibly do this:

```{bash}
# change permission to make file an executable
chmod u+x ~/PyFan/bin/pull_repos
chmod u+x ~/PyFan/bin/push_repos
# execute script
bash ~/PyFan/bin/pull_repos
```

### 2020-01-12 nontex/install/linux/fn_vim.Rmd
repo pull bash update, sublime to path

- Copy current word: *dw*
- Copy from cursor to end of line (need to set this): *y$* or *Y*
- Copy until end of paragraph: *yip*
- Copy all text on page: *ggVGY*

>>>>

- Copy current word: *yiw*; or *yw* which yanks word from current letter to end
- Copy from cursor to end of line (need to set this): *y$* or *Y*
- Copy until end of paragraph: *yip*
- Copy all text on page: *ggVGY*

### 2020-01-12 nontex/install/windows/fn_installations.Rmd
repo pull bash update, sublime to path

# install additional packages
conda install -y statsmodels datashape seaborn
conda install -c conda-forge -y interpolation awscli
conda install -c anaconda -y boto3
```

@@

>>>>

# install additional packages
# linux utilites
conda install -y m2-base 
# stats and graphs
conda install -y statsmodels datashape seaborn
# various
conda install -c conda-forge -y interpolation awscli
# aws communicate
conda install -c anaconda -y boto3
```

@@

Put sublime path in windows path for example:

```
C:\Program Files\Sublime Text 3\
```
